### 2021-04-20 Chapter-2/Chapter-2.tex
Updates from Overleaf

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses in the dissertation. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing and aligning different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} uses mutual information (MI) between sensitive input and execution state to detect side-channels.

@@

\section{Trace-based Binary Analysis}
Trace-based binary analysis can be seen as a type of dynamic analysis. It 
analyzes one concrete program path one time rather than trying to cover
as many paths as possible. Compared to static analysis, trace-based analysis
is usually more precise as it can use runtime information. It usually has
two steps. The first step is collecting trace information. Existing
approaches usually often rely on binary instrumentation frameworks or emulators (e.g, Intel Pin~\cite{luk2005pin},
Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
as symbolic execution, taint analysis. Depending on when the analysis is launched,
there are two kinds of trace-based analysis, online analysis and offline analysis.
As the name suggests, online analysis is performed at runtime. The target program's
data can be modified directly in memory, which is useful in fuzzing because the analysis
can force the program to go through into a specific branch. Contrary to online analysis,
offline analysis or post analysis happens when the program finish executions. 
Trace-based binary analysis has been adopted in several tasks like algorithm
detection, vulnerability detection and malware analysis. We only mention a few of
most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bit-wise symbolic execution, which can
identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use 
system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
perform an offline analysis on execution traces to identify heap overflows.

There are several known binary analysis frameworks that can ease users 
to launch analysis on binary executable. BitBlaze~\cite{brumley2011bap} is a binary analysis platform
that provides both the static and dynamic analysis. It uses tracecap plugin to 
collect execution trace and convert the trace into Vine IR. Binary Analysis Platform (BAP)
is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
binary analysis platform recently, also support trace-based analysis. It first convert
each instruction into VEX IR and interpret each IR in Python.

Above existing well-known binary analysis frameworks all adopt the IR layer, which make
it easy to implement the framework and support multiple architectures. However, it can have
a very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables
are involved or not. Besides, as side-channels are low level problems in general, the IR
design will also lose some information. For example, IR-level branches are not necessarily 
a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into
non-branch instructions like conditional moves. Those above limitations motivate us to
implement a new trace-based binary analysis framework.

>>>>

The dynamic approach, usually consists of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get the formula of each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses in the dissertation. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing and aligning different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach from DATA by comparing all accessed addresses. It uses mutual information (MI) between sensitive input and execution state to quantify the information.

@@

\section{Trace-based Binary Analysis}
Trace-based binary analysis can be seen as a type of dynamic analysis. It 
analyzes one concrete program path one time rather than trying to cover
as many paths as possible. Compared to static analysis, trace-based analysis
is usually more precise as it can incorporate the runtime information. It usually has
two steps. The first step is collecting trace information. Existing
approaches usually often rely on binary instrumentation frameworks or emulators (e.g, Intel Pin~\cite{luk2005pin},
Valgrind~\cite{nethercote2007valgrind}, QEMU). The second step is analyzing the trace using techniques, such
as symbolic execution, taint analysis. Depending on when the analysis is launched,
there are two kinds of trace-based analysis, online analysis and offline analysis. As the name suggests, online analysis is performed during the program execution. The target program's data can be modified directly in memory, which is useful to tasks like fuzzing because the analysis
can force the program to execute a specific branch. Contrary to online analysis,
offline analysis or post analysis happens when the program finish executions. 
Trace-based binary analysis has been adopted in several tasks like algorithm
detection, vulnerability detection and malware analysis. We only mention a few of
most related works here. Xu et al.~\cite{xu2017cryptographic} introduce bit-wise symbolic execution, which can
identify crypto algorithms in obfuscated binaries. Ming et al.~\cite{ming2017binsim} use 
system call sliced segment equivalence checking to do binary diffing. Jia et al.~\cite{jia2017towards}
perform an offline analysis on execution traces to identify heap overflows.

There are several known binary analysis frameworks that can ease users to launch analysis on binary executable. BitBlaze~\cite{brumley2011bap} is a binary analysis platform that provides both the static and dynamic analysis. It uses the tracecap plugin to  collect execution trace and convert the trace into Vine IR. Binary Analysis Platform (BAP)
is an another binary analysis platform. Similar to BitBlaze, it use a Pintrace tool to
collect execution trace and convert the trace into BAP IR. Angr~\cite{shoshitaishvili2016state}, the most popular
binary analysis platform recently, also support trace-based analysis. It converts each instruction into VEX IR and interprets each IR in Python.

Above existing well-known binary analysis frameworks all adopt the IR layer, which make it easy to implement the analysis and support multiple architectures. However, it can have a very low efficiency and long traces. All IR must be interpreted no matter if symbolic variables are involved or not. Besides, as side-channels are low level problems in general, the IR design will also lose some information. For example, IR-level branches are not necessarily  a super-set or a sub-set of machine-code level branches. Some IR-level branches can be compiled into non-branch instructions like conditional moves. Those above limitations motivate us to implement a new trace-based binary analysis framework.

### 2021-04-20 Chapter-3/Chapter-3.tex
Updates from Overleaf

Recent work has made good progress in detecting side-channel leakages automatically. Some tools (e.g., CacheD, CaSym) have successfully identified unknown leakage sites from software products automatically. However, those tools have the following limitations.

First, although some tools can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead. As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually. The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites). More importantly, if many leakage sites are on the trimmed code, those tools will miss those leakage sites as well.

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches is not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products. Different from previous methods, our tool analyzes on the machine code, which can give more precision than traditional IR-based approaches.  We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems. The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages. Compared to recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks. In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.

@@

During the evolution of the modern computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply. As a result, modern CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory. By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

@@

\subsection{Threat Model}
We assume that an attacker shares the same hardware platform with the target.
The attacker attempts to retrieve sensitive information through address-based
side-channel attacks. The attacker has no direct access to the target's memory or cache, but he can probe the memory or cache at each program point. Here are a few examples.
\begin{enumerate}
  \item A host machine has several Virtual Machines (VMs). The victim runs the application inside one VM. An attacker can control the VM and probe the process running on the other VM.
  \item  In a shielding system, a malicious operating system can extract sensitive information from protected user-level applications.
  \item A ring-3 application can probe some sensitive information inside the kernel.
\end{enumerate}

In reality, attackers will face many possible obstacles, such as the noisy observations of the memory or cache. However, for this project, we assume
the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks. We only consider deterministic programs and assume an attacker has access to the source code or binary executable of the target program.

@@

$PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = 0$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = 0$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

@@

\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
Symbolic execution is notorious for its high performance cost.
Previous trace-oriented symbolic execution
work~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} has serious
performance bottlenecks. As a result, these approaches either apply only to
small programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or require
domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis.
Those tools interpret each
instruction and update memory cells and registers with formulas that
captured the semantics of the execution and search different input values that
can lead to different execution behaviors using constraint solver.
We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas. While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
We observe that finding side-channels using symbolic execution differs from
traditional symbolic execution, and it can be optimized to be as efficient
as other methods.

@@

\begin{table}[ht]
  \centering\small\footnotesize
  \caption{The number of x86,  % instructions and the number of 
    REIL IR, and VEX IR instructions on the traces of crypto programs.}
  \label{scala:ir}
  \resizebox{.7\columnwidth}{!}{%

@@

\section{Design and Implementation}
\subsection{Trace Logging}
The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI).
We run a program with the concrete input under the DBI to record execution traces.
The trace data has the following information:
\begin{itemize}
  \item Each instruction mnemonics and its memory address.
  \item The operands of each instruction and their concrete values during the runtime.
  \item The value of EFLAGS register.
  \item The memory address and the length of the sensitive information.
        Most crypto libraries stores sensitive information in arrays,
        variables or contiguous buffer.
\end{itemize}

@@

\begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

\subsubsection{Information Flow Check}
\detect{} is designed to help software developers find and understand the side-channel vulnerabilities. To ease the procedure of fixing the bug, we also track the information flow for each byte of the input
buffer.
The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
At the beginning of the analysis, \detect{} keep track for each byte in
the original buffer. When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memory. If the value is concrete, it means the instruction has nothing to do with the original buffer.
If the value is a formula, it means the original information passes through the instruction. Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \detect{} can know which byte in the origin buffer goes through the instruction.

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a crytpographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.

@@

We build the source program into 32-bit x86 Linux executables with GCC 7.5
running on Ubuntu 16.04. While our tool can work on the stripped binaries, 
in the evaluation, we keep the debug information to get the fine-grained infromation
(e.g., line numbers).
We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
RAM. We run the experiments simultaneously, but the execution time is calculated on a single-core.

During our evaluation process, we are interested in the following
aspects:
\begin{enumerate}
    \item Is \detect{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
    \item How much performance overhead does the method introduce? (Performance)
    \item How effective are the design choices made by the tool method? (Design Choices)
\end{enumerate}

@@

\detect{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also has the common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed.However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above point. For symmetric encryption, during our evaluation there is no secret-dependent control-flow transfers. RSA implementations have several secret-dependent control-flow transfers. Most of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.

We use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

>>>>

Recent work has made good progress in detecting side-channel leakages automatically. Some tools (e.g., CacheD~\cite{203878}, CaSym~\cite{Brotzman19Casym}) have successfully identified unknown leakage sites from software products automatically. However, those tools have the following limitations.

First, although some tools~\cite{Brotzman19Casym} can find side-channel leakages in real-world software products, they can only analyze one code fragment at a time due to the expensive performance overhead. As a result, users of those tools sometimes need to cut off some irrelevant code based on their experience manually. The trimming process is tedious and needs domain knowledge of the target software (e.g., which part of the code is more likely to have side-channel leakage sites). More importantly, if serious leakage sites are on the trimmed code, those tools will miss those leakage sites as well.

Second, many tools perform the analysis at the level of intermediate representations (IR) instead of the machine code. It is a design decision to facilitate the implementations. While analyzing the IRs can simplify the implementation, it is not a suitable design choice for the side-channel analysis. In reality, side-channel leakages are a pretty low-level issue and only the low-level analysis can give the most accurate results. For example, the IR-level branches are not necessarily a superset or a subset of machine-code level branches. Besides, compiler optimizations can eliminate the IR-level branches like conditional moves and the converse could also happen. Moreover, translating the machine code into IRs can cause a significant overhead for the trace analysis, as we will discuss in the dissertation.

To overcome the above problems, we propose a fast and precise method to detect the side-channel leakages in real-world software products. We examine the bottleneck of current symbolic execution approaches and optimize it to work on real-world cryptography systems. Different from previous methods, our tool analyzes the machine instructions, which can give more precision than traditional IR-based approaches. We evaluate our tool on popular cryptography libraries including OpenSSL, mbedTLS, Libgcrypt, and Monocypher. The evaluation results show that our tool can identify previous side-channel leakages, as well as find new leakages. Compared with recent tools, our tool is 3-100x faster while finding all the leakages when we evaluate on the same benchmarks. In addition, our tool finds new side-channel vulnerabilities that are missed by the previous work.

@@

During the evolution of the computer architecture, researchers find that CPUs process data in a much faster speed than the main memory (DRAM) can supply. As a result, CPUs adopt a hierarchy memory architecture to bridge the performance gap between the CPUs and the main memory. By storing extra copies of recently accessed data and code in a smaller but faster memory, the software can get its most recently accessed code and data in a shorter time.

@@

\subsection{Threat Model}
We assume that an attacker shares the same hardware platform with the victim.
The attacker attempts to retrieve sensitive information through address-based side-channel attacks. The attacker has no direct access to the victim's data, but he can probe the memory or cache at each program point. Here are a few examples.
\begin{enumerate}
  \item A host machine has several virtual machines (VMs). The victim runs the application inside one VM. An attacker can control one VM and probe the process running on the other VM.
  \item  In a shielding system~\cite{arnautov2016scone,schuster2015vc3}, a malicious operating system can extract sensitive information from protected user-level applications.
  \item A ring-3 application can probe some sensitive information inside the kernel.
\end{enumerate}

In reality, attackers may face many possible obstacles, such as the noisy observations of the memory or cache. However, for this project, we assume the attacker has noise-free observations as in previous work~\cite{203878,182946,Brotzman19Casym}. The threat model captures most address-based side-channel attacks and apply to the three attack models: 1) time-based attacks, 2) access-based attacks, 3) trace-based attacks. We only consider deterministic programs and assume an attacker has access to the source code or binary executable of the target program.

@@

$PC$ represents the path condition. An adversary can observe which branch the code executes if the branch condition
equals $t_b$. We use the constraint $c_i : f_i(\beta, k, m) = t_b$ to model
the observation ($o$) on secret-dependent control-transfers. Note that in the
above definition, $m$ is also a variable. So it is possible for some $m \in M$,
we can not find a pair of two different $k_{i1}$ and $k_{i2}$ to satisfy the above inequation. For example, in Figure~\ref{fig:chapter3:cf}, if $m = \mathtt{0}$, the function \textsf{example1} will always execute the branch 2. However, if $m = \mathtt{0xffffffff}$ and $k = \mathtt{0}$, the function \textsf{example1} executes the branch 1 and the function \textsf{example1} executes the branch 2 when $k = \mathtt{0xf000000}$.

@@

\section{Scalability}
\subsection{Trace-oriented Symbolic Execution}
Symbolic execution is notorious for its expensive performance cost.
Previous trace-oriented symbolic execution
work~\cite{203878,Chattopadhyay:2017:QIL:3127041.3127044} has serious
performance bottlenecks. As a result, these approaches either apply only to
small programs~\cite{Chattopadhyay:2017:QIL:3127041.3127044} or require
domain knowledge~\cite{Wang:2007:NCD:1250662.1250723} to simplify the analysis.
Those tools interpret each
instruction and update memory cells and registers with formulas that
captured the semantics of the execution and search different input values that
can lead to different execution behaviors using constraint solver.
We implement the approach presented in \S\ref{chapter3:method} and model the side-channels as formulas. While the tools can analyze some simple cases such as AES, it cannot handle complicated examples such as RSA.
We observe that finding side-channels using symbolic execution differs from
traditional symbolic execution, and it can be optimized to be as efficient
as other methods.

@@

\begin{table}[ht]
  \centering\small\footnotesize
  \caption{The number of x86,  % instructions and the number of 
    REIL IR, and VEX IR instructions on the traces of crypto programs.}
  \label{scala:ir}
  \resizebox{.8\columnwidth}{!}{%

@@

\section{Design and Implementation}
\subsection{Trace Logging}
The trace information can be logged via some emulators (e.g., QEMU) or dynamic binary instrumentation tools (DBI).
In this work, we run a program with the concrete input under the DBI to record execution traces.
The trace data has the following information:
\begin{itemize}
  \item Each instruction mnemonics and its memory address.
  \item The operands of each instruction and their concrete values during the runtime.
  \item The value of EFLAGS register.
  \item The memory address and the length of the sensitive information.
        Most crypto libraries stores sensitive information in arrays,
        variables or contiguous buffer.
\end{itemize}

@@

\begin{lstlisting}[xleftmargin=.3\textwidth, xrightmargin=.2\textwidth, frame=none][ht]
...
0x0000e781      add dword [local_14h], 1
0x0000e785      cmp dword [local_14h], 4
0x0000e789      jne 0xe7df
0x0000e78b      mov dword [local_14h], 0
...
\end{lstlisting}

@@

\subsubsection{Information Flow Check}
\detect{} is designed to help software developers find and understand the side-channel vulnerabilities. To ease the procedure of fixing bugs, we also track the information flow for each byte of the input
buffer.
The step can be seen as the multiple-tag taint analysis. With the help of the information from symbolic execution, we can implement a relatively simple but relatively precise information flow track.
At the beginning of the analysis, \detect{} keep track of each byte in
the original buffer. When \detect{} symbolically executes each instruction in the trace, it will check every value read from registers or memory. If the value is concrete, it means the instruction has nothing to do with the original buffer.
If the value is a formula, it means the original information passes through the instruction. Since each byte in the sensitive buffer is represented as a symbol with a unique ID, \detect{} can know which byte in the origin buffer goes through the instruction.

\section{Evaluation}
We evaluate our method on real-world crypto libraries, which include  OpenSSL, mbedTLS, Libgcrypt and Monocypher\@. OpenSSL is the most commonly used crypto libraries in today's software. mbedTLS\@ (previous known as PolarSSL) is designed to be easy to understand and fit on embedded devices. We also evaluate Monocypher, a new cryptographic library that resists to most side-channel attacks.
According to the developers, Monocypher is designed to have no secret dependent indices and secret dependent branches. Therefore, Monocypher should be secure under our threat model. Libgcrypt is a cryptographic library from the GunPG. As some previous work (e.g., CacheD) choose to evaluate their tools on CacheD, we can compare the evaluation results by applying the tool on Libgcrypt.

@@

We build the source program into 32-bit x86 Linux executables with GCC 7.5
running on Ubuntu 16.04. While our tool can work on the stripped binaries, 
in the evaluation, we keep the debug information to get the fine-grained information
(e.g., line numbers).
We run our experiments on a 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB
RAM. We run the experiments simultaneously, but the execution time is calculated on a single-core.

During our evaluation process, we are interested in the following
aspects:
\begin{enumerate}
    \item Is \detect{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
    \item How much performance overhead does the method introduce? (Performance)
\end{enumerate}

@@

\textbf{Coverage.} \detect{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed. However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above intuition. For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation. RSA implementations have several secret-dependent control-flow transfers. Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result shows that it is spending most its time in Z3. Later, we use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

\textbf{Cache Model.} We use a simple cache model in this work. Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache. First, there is no fundamental difficulties for us to adopt a more realistic cache models. Second, the LRU model is still a substantial simplification of a real cache. However, the choice of a logical model of cache can bring expensive overheads.

\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze those leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages.
